---
title: "Homework 6"
output: github_document
---

```{r setup, echo = FALSE, message = FALSE, warning = FALSE}
library(tidyverse)
library(p8105.datasets)
library(readr)
library(purrr)
library(modelr)
library(mgcv)
library(ggplot2)
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = 0.6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
set.seed(1)
```


##Problem 1 

```{r create dataset_1,  message = FALSE, warning = FALSE}
homicide_df = 
  read_csv("data/homicide-data.csv", na = c("", "NA", "Unknown")) %>% 
    mutate(
        city_state = str_c(city, state, sep = "_"),
        victim_age = as.numeric(victim_age),
        resolution = case_when(
        disposition == "Closed without arrest" ~ 0,
        disposition == "Open/No arrest"        ~ 0,
        disposition == "Closed by arrest"      ~ 1,
      )
    ) %>% 
  filter(
    !city_state %in% c("Tulsa_AL", "Dallas_TX", "Phoenix_AZ", "Kansas City_MO"),
    victim_race %in% c("Black", "White")    
    ) %>% 
  select(city_state, resolution, victim_age, victim_race, victim_sex)
```

Start with one city 

```{r regress_1}
baltimore_df = 
  homicide_df %>% 
  filter(city_state == "Baltimore_MD")
glm(resolution ~ victim_age + victim_race + victim_sex, 
    data = baltimore_df,
    family = binomial()) %>% 
  broom::tidy() %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(term, OR, starts_with("CI")) %>% 
  knitr::kable(digits = 3)
```

Do it for every city in the dataset.
First nest the dataset and then fit the dataset for each city.

```{r simulate_1}
models_results_df =
homicide_df %>%
  nest(data = -city_state) %>% 
  mutate(
    models = map(.x = data, ~glm(resolution ~ victim_age + victim_race + victim_sex, data = .x,
                                family = binomial())),
    results = map(models, broom::tidy)
  ) %>% 
  select(city_state, results) %>% 
  unnest(results) %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(city_state, term, OR, starts_with("CI"))
```

### Make a plot of the ORs

In each of these 50 cities are male homicide victims more or less likely to have homicide resoled by arrest compared to female victims

```{r plot_1}
models_results_df %>% 
  filter(term == "victim_sexMale") %>% 
  mutate(city_state = fct_reorder(city_state, OR)) %>% 
  ggplot(aes(x = city_state, y = OR)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper)) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

## Problem 2 
Read in the data

```{r import_tidy_baby, message = FALSE}
baby_df = 
  read_csv("./data/birthweight.csv") %>% 
  mutate(
    babysex = as_factor(babysex),
    frace = as_factor(frace),
    malform = as_factor(malform),
    mrace = as_factor(mrace),
    parity = as_factor(parity),
    pnumsga = as_factor(pnumsga),
    prior_lbw = case_when(
      pnumlbw == 0 ~ 0,
      pnumlbw > 0  ~ 1
    ),
    prior_lbw = as_factor(prior_lbw)
  )
```
The birthweight data contains `r bw_df %>% nrow()` rows, and no missing data.

#### Fit the models

We will compare three models: a crude model(m1) with just length and gestational weeks; an interactions model(m2) with head circumference, length, sex, and all interactions (including 3-way); and a full model(m3), that includes head circumference, length, sex, mother's race, family income, presence of malformations, and the interaction of mother's pre-pregnancy weight and her gestational weight. 

```{r models, message = FALSE}
model_m1 = lm(bwt ~ blength + gaweeks, data = baby_df)
model_m2 = lm(bwt ~ bhead * blength * babysex, data = baby_df)
model_m3 = lm(bwt ~ bhead + blength + babysex + mrace + fincome + malform + delwt * ppwt, 
                data = baby_df)
```

We will now create the residuals and predicted values for each model. 

```{r resid, message = FALSE}
m1_df = 
  baby_df %>% 
  modelr::add_residuals(model_crude) %>% 
  modelr::add_predictions(model_crude)
  
m2_df = 
  baby_df %>% 
  modelr::add_residuals(model_inter) %>% 
  modelr::add_predictions(model_inter)
m3_df = 
  baby_df %>% 
  modelr::add_residuals(model_full) %>% 
  modelr::add_predictions(model_full)
```

Plotting the residuals and predicted values for each model.

```{r resid_plots, message = FALSE}
m1_resid_plot = 
  m1_df %>% 
  ggplot(aes(x = resid, y = pred)) +
  geom_point(alpha = 0.5) +
  xlim(-2000, 5000) +
  ylim(-1000, 5000) +
  labs(
    title = "Predicted values on residuals for crude model",
    x = "Residuals",
    y = "Predicted values"
  )
m2_resid_plot = 
  m2_df %>% 
  ggplot(aes(x = resid, y = pred)) +
  geom_point(alpha = 0.5) +
  xlim(-2000, 5000) +
  ylim(-1000, 5000) +
  labs(
    title = "Predicted values on residuals for interaction model",
    x = "Residuals",
    y = "Predicted values"
  )
m3_resid_plot = 
  m3_df %>% 
  ggplot(aes(x = resid, y = pred)) +
  geom_point(alpha = 0.5) +
  xlim(-2000, 5000) +
  ylim(-1000, 5000) +
  labs(
    title = "Predicted values on residuals for full model",
    x = "Residuals",
    y = "Predicted values"
  )
m1_resid_plot
m2_resid_plot
m3_resid_plot
```

The interaction and full models are very similar, the crude model has much larger residuals and predicted values. Thus, the crude model is likely a poorer fit for the data.

We will do soe cross-validation now to understand more- 

```{r cv, message = FALSE}
cv_df =
  crossv_mc(baby_df, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    text = map(test, as_tibble),
    m1_mod = map(.x = train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    m2_mod = map(.x = train, ~lm(bwt ~ bhead * blength * babysex, data = .x)),
    m3_mod = map(.x = train, ~lm(bwt ~ bhead + blength + babysex + mrace + fincome + 
                                    malform + delwt * ppwt, data = .x)),
    rmse_m1 = map2_dbl(.x = m1_mod, .y = test, ~rmse(model = .x, data = .y)),
    rmse_m2 = map2_dbl(.x = m2_mod, .y = test, ~rmse(model = .x, data = .y)),
    rmse_m3 = map2_dbl(.x = m3_mod, .y = test, ~rmse(model = .x, data = .y))
  )
cv_plot = 
  cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model",
    names_prefix = "rmse_",
    values_to = "rmse"
  ) %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) +
  geom_violin()
cv_plot
```

The full model(model 3) will be the best fir for data because it has the lowest root mean squared error (rmse).





















